---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# redditr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/geoffwlamb/redditr.svg?branch=master)](https://travis-ci.org/geoffwlamb/redditr)
[![Coverage status](https://codecov.io/gh/geoffwlamb/redditr/branch/master/graph/badge.svg)](https://codecov.io/github/geoffwlamb/redditr?branch=master)
<!-- badges: end -->

## Overview
redditr is an R package intended to help obtain content from Reddit by interfacing with the <a href = "https://github.com/pushshift/api"> pushshift.io Reddit API</a>.

The immediate scope of this package is to provide functionality for importing Reddit comment and post data into R. Some additional functionality is provided for handling time-based information. Aside from that, redditr will not try to do any general text or data cleaning. Other, far more established packages are better options for handling text data once it's been imported into R.

Let's see how this goes...

## Installation
Install via devtools:
```{r install redditr, eval=FALSE}
devtools::install_github("geoffwlamb/redditr")
```


## Examples
The redditr package's flagship function, <code>get_reddit_content</code>, takes [Pushshift.io API Search Parameters](https://github.com/pushshift/api#search-parameters-for-comments) as arguments and returns a data.frame with information related your query. Here are some ideas for how you can use this function:

``` {r examples}
# load redditr
library(redditr)
```

<br>
<hr>
<br>

Hopefully that captures the essence of what this package aims to accomplish. At some point, I'll add a bit more error handling to ensure the validity of constructed urls, but in the meantime, please experiment with the parameters <a href = "https://github.com/pushshift/api#search-parameters-for-comments"> here</a> (and feel free to let me know if anything isn't working well).

Thanks for checking out redditr!
